---
title: "Final Project"
author: "Christopher Loan"
date: "5/24/2021"
output: html_document
---

Definitely:

o	number of level 1 units, 
o	number of level 2 units, 
o	magnitude of interaction effect, 
o	comparing these models to the equivalent model in lmer/nlme that doesn’t look for parameter instability

Maybe:

o	cross-level interaction vs. same-level interaction, (probably lower power for cross level)
o	ICC, 
o	continuous vs. categorical interaction terms, 
o	number of level 3 units,
o	nested vs. cross-classified designs, 
o	continuous vs. categorical outcomes, 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## https://benwhalley.github.io/just-enough-r/power-analysis.html
```

```{r}
library(tidyverse)
library(glmertree)
library(dials)
source(here::here('Scripts', 'functions_EDLD629_Final.R'))
```

```{r}
intx_values <- c(-1.25, -0.75, 0, 0.75, 1.25)
```

```{r cache = T}
final_results <- 
  make_final_results(
    intx_values = intx_values, 
    num_df = 1000, 
    n_range = c(40, 200), 
    j_range = c(3, 20), 
    intercept_lv1 = 4.00, 
    main_x = 1.25, 
    main_z = 1.00,
    residual_var_sd_lv1 = 6.00,
    random_int_mean_lv2 = 5, 
    random_int_sd_lv2 = 2.00
    )
```

```{r cache = T}
ests <- extract_sim_ests(final_results)
perf <- extract_sim_perfomance(final_results)
fit_plots <- extract_sim_fit_plots(final_results)
sim_density <- extract_sim_ests_density(final_results)
```

```{r}
ests 
```

```{r}
ggpubr::ggarrange(
  map(
  map(
    fit_plots, 
    ~.x + 
      labs(
        x = NULL, 
        y = NULL#, 
        #caption = NULL
        ) + 
      theme_minimal(base_size = 20)
  ),
  ~.x
  )
)


```

```{r}
ggpubr::ggarrange(
  sim_density$`-1.25` + theme_minimal(base_size = 15),
  sim_density$`-0.75` + theme_minimal(base_size = 15),
  sim_density$`0` + theme_minimal(base_size = 15), 
  sim_density$`0.75` + theme_minimal(base_size = 15),
  sim_density$`1.25` + theme_minimal(base_size = 15),
  common.legend = T, 
  legend = 'bottom', 
  ncol = 1, 
  )
```

```{r}
ggpubr::ggarrange(
  fit_plots$`-1.25` + theme_minimal(base_size = 15),
  fit_plots$`-0.75` + theme_minimal(base_size = 15),
  fit_plots$`0` + theme_minimal(base_size = 15), 
  fit_plots$`0.75` + theme_minimal(base_size = 15),
  fit_plots$`1.25` + theme_minimal(base_size = 15),
  common.legend = T, 
  legend = 'bottom', 
  ncol = 1
  )
```


```{r}
map2_dfr(
  .x = rep(as.character(intx_values), 2),
  .y = c(rep('lmer', 5), rep('tree', 5)), 
  ~c_intervals(final_results, intx_level = .x, which_model = .y)
  ) %>% 
  mutate(
    model = c(rep('lmer', 5), rep('tree', 5)), 
    intx_level = rep(intx_values, 2)) 
```

