---
title: "Final Project"
author: "Christopher Loan"
date: "5/24/2021"
output: html_document
---

Definitely:

o	number of level 1 units, 
o	number of level 2 units, 
o	magnitude of interaction effect, 
o	comparing these models to the equivalent model in lmer/nlme that doesn’t look for parameter instability

Maybe:

o	cross-level interaction vs. same-level interaction, (probably lower power for cross level)
o	ICC, 
o	continuous vs. categorical interaction terms, 
o	number of level 3 units,
o	nested vs. cross-classified designs, 
o	continuous vs. categorical outcomes, 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## https://benwhalley.github.io/just-enough-r/power-analysis.html
```

```{r}
library(tidyverse)
library(lme4)
library(equatiomatic)
library(sundry)
library(glmertree)
#library(simr)
source('Scripts/functions_EDLD629_Final.R')
```

## simulate multilevel data

```{r}
dat <-
  simulate_two_level_interaction(
  n = 100, 
  j = 50, 
  intercept_lv1 = 10.00, 
  interaction = 5.00,
  main_x = 1.00, 
  main_z = 2.00,
  residual_var_sd_lv1 = 6.00,
  random_int_mean_lv2 = 5, 
  random_int_sd_lv2 = 2.00, 
  start_seed = 123
  )

#dat %>% psych::describe()
```

```{r}
tree1 <- 
  lmertree(
  data = dat, 
  formula = 
    score ~ 
    x_lv1 |
    (1 | scid) | 
    z_lv1, 
  bonferroni = T,
  alpha = 0.001
)
```

```{r}
tree2 <- 
  lmertree(
  data = dat, 
  formula = 
    score ~ 
    x_lv1 + z_lv1 |
    (1 | scid) | 
    z_lv1, 
  bonferroni = T,
  alpha = 0.001
)
```

```{r}
coef(tree1)

sum1 <- 
  summary(tree1$tree)[[1]]

coef(sum1)

sum11 <- 
  sum1$coefficients

temp <- 
  summary(tree1$tree)[[1]][['coefficients']]

plot(tree1)
coef(tree1)

arm::se.coef(tree1$tree)$fixef
```

```{r}
lmer1 <- 
  lmer(
  data = dat, 
  formula = 
    score ~ 
    x_lv1*z_lv1 + (1 | scid)
)
summary(lmer1)
```

```{r}
rmse(tree1)
rmse(lmer1)
AIC(tree1)
AIC(lmer1)
BIC(tree1)
BIC(lmer1)
```

```{r}
get_node_counts(tree1) 
```

```{r}
extract_node_splits(tree1)
```

```{r}
get_number_of_nodes(tree1)
```

```{r}
extract_variable_ranges(glmertree_mod = tree1)
```



```{r}
tree1$data %>% 
  mutate(
    node = .tree, 
    prediction = predict(tree1), 
    id = 1:nrow(.)
    ) %>% 
  ggplot(
    aes(x = x_lv1, y = prediction, color = node)
  ) +
  geom_point(
    #aes(size = abs(prediction - score)), 
    alpha = 0.2
    ) +
  geom_smooth(method = 'lm', se = F, color = 'black', aes(group = node)) +
  geom_smooth(
    inherit.aes = F, 
    aes(x = x_lv1, y = prediction), 
    color = 'black', 
    se = F, 
    method = 'loess')
```

```{r}
tree1$data %>% 
  mutate(
    node = .tree, 
    prediction = predict(tree1), 
    id = 1:nrow(.)
    ) %>% 
  ggplot(
    aes(x = z_lv1, y = prediction, color = node)
  ) +
  geom_point(
    #aes(size = abs(prediction - score)), 
    alpha = 0.2
    ) +
  geom_smooth(method = 'lm', se = F, color = 'black', aes(group = node)) +
  geom_smooth(
    inherit.aes = F, 
    aes(x = z_lv1, y = prediction), 
    color = 'black', 
    se = F, 
    method = 'loess')
```


```{r}
library(dials)

ns_param <- 
  new_quant_param(
    type = "integer",
    range = c(10, 2000),
    inclusive = c(TRUE, TRUE),
    trans = NULL,
    label = c(ns_param = "number of level 1 units"),
    finalize = NULL
  )

js_param <- 
  new_quant_param(
    type = "integer",
    range = c(10, 200),
    inclusive = c(TRUE, TRUE),
    trans = NULL,
    label = c(js_param = "number of level 2 units"),
    finalize = NULL
  )

intx_param <- 
  new_quant_param(
    type = "integer",
    range = c(-3, 3),
    inclusive = c(TRUE, TRUE),
    trans = NULL,
    label = c(intx_param = "interaction values"),
    finalize = NULL
  )
```

```{r}
parameter_grid <- 
  grid_max_entropy(
  ns_param, 
  js_param, 
  intx_param,
  size = 100,
  original = FALSE)
```

```{r}
## make 100 data sets with a space filling design to cover all of these
sim_dat <-
  pmap(
    list(
      parameter_grid$ns_param, 
      parameter_grid$js_param, 
      parameter_grid$intx_param), 
    ~simulate_two_level_interaction(
      n = ..1, 
      j = ..2, 
      intercept_lv1 = 10.00, 
      interaction = ..3,
      main_x = 1.00, 
      main_z = 2.00,
      residual_var_sd_lv1 = 6.00,
      random_int_mean_lv2 = 5, 
      random_int_sd_lv2 = 2.00, 
      start_seed = 123
      )
  )
```

