---
title: "Scratch Work"
author: "Christopher Loan"
date: "5/24/2021"
output: html_document
---

Definitely:

o	number of level 1 units, 
o	number of level 2 units, 
o	magnitude of interaction effect, 
o	comparing these models to the equivalent model in lmer/nlme that doesn’t look for parameter instability

Maybe:

o	cross-level interaction vs. same-level interaction, (probably lower power for cross level)
o	ICC, 
o	continuous vs. categorical interaction terms, 
o	number of level 3 units,
o	nested vs. cross-classified designs, 
o	continuous vs. categorical outcomes, 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## https://benwhalley.github.io/just-enough-r/power-analysis.html
```

```{r}
library(tidyverse)
library(lme4)
#library(equatiomatic)
#library(sundry)
library(glmertree)
#library(simr)
library(dials)
source('Scripts/functions_EDLD629_Final.R')
```

## simulate multilevel data

```{r}
dat <-
  simulate_two_level_interaction(
  n = 50, 
  j = 100, 
  intercept_lv1 = 10.00, 
  interaction = 2.00,
  main_x = 0, 
  # this makes the models more equivalent
  main_z = 0,
  residual_var_sd_lv1 = 6.00,
  random_int_mean_lv2 = 5, 
  random_int_sd_lv2 = 2.00, 
  start_seed = 123
  )

#dat %>% psych::describe()
```

```{r}
tree1 <- 
  lmertree(
  data = dat, 
  formula = 
    score ~ 
    x_lv1 |
    (1 | scid) | 
    z_lv1, 
  cluster = scid
)

get_glmertree_moderation(tree1, which_variable = 'x_lv1', mean_only = T)

```

```{r}
lmer1 <- 
  lmer(
  data = dat, 
  formula = 
    score ~ 
    x_lv1*z_lv1 + (1 | scid)
)
summary(lmer1)
```

```{r}
tree2 <- 
  lmertree(
  data = dat, 
  formula = 
    score ~ 
    x_lv1 + z_lv1 |
    (1 | scid) | 
    z_lv1, 
  cluster = scid
)
```

```{r}
node_coefs <- tibble(
  node = rownames(fixef(tree1)),
  'fixed_intercept' = fixef(tree1)[, 1], 
  'beta_x_lv1'= fixef(tree1)[, 2]#, 
  #'beta_z_lv1'= fixef(tree1)[, 3]
  )

temp <- 
  tree1$data %>% 
  left_join(node_coefs, by = c('.tree' = 'node')) %>% 
  mutate(
    y_hat = predict(tree1), 
    resid = residuals(tree1)
    ) 

# temp %>% 
#   mutate(
#     intercept = fixed_intercept + .ranef,
#     mod = x_lv1*z_lv1,
#     numerator = score - intercept - beta_x_lv1*x_lv1 - resid,
#     estimated_intx = numerator/mod
#     ) %>% 
#   arrange(estimated_intx)
#   #filter(.tree == 4)
#   group_by(.tree) %>%
#   summarize(
#     average_intx = mean(estimated_intx),
#     se_intx = sd(estimated_intx)/sqrt(n()))





temp
## this works, so I'm not sure why the other doesn't
#(temp$y_hat - temp$intercept - temp$beta_x_lv1*temp$x_lv1)/(temp$x_lv1*temp$z_lv1)
weighted.mean(x = temp$average_intx, w = get_node_counts(tree1)$n)
plot(tree1, 'tree', ask=F)
```

```{r}
tree1$lmer %>% summary()
tree_temp <- 
  tibble(
    fixed_effects = fixef(tree1$lmer),
    names = names(fixef(tree1$lmer))
    ) %>% 
  slice(
    4:6
  )

weighted.mean(
  tree_temp$fixed_effects, 
  w = get_node_counts(tree1)$n
  )

sd(tree_temp$fixed_effects)/sqrt(length(get_node_counts(tree1)$n))


avg_mod<- tibble(
  fx = tree_temp$fixed_effects, 
  fx2 = lag(fx)
  ) %>% 
  mutate(diff = fx2-fx) %>% 
  pull(diff)

mean(avg_mod,na.rm = T)
sd(avg_mod, na.rm = T)/sqrt(length(avg_mod)-1)

```

```{r}
tree2 <- 
  lmertree(
  data = dat, 
  formula = 
    score ~ 
    x_lv1 + z_lv1 |
    (1 | scid) | 
    z_lv1, 
  bonferroni = T,
  alpha = 0.001
)
```

```{r}

temp_df <- 
  tibble(
    k = get_num_fixed_effects(tree1),
    n = get_node_counts(tree1)[, 2],
    se = get_standard_errors(tree1),
    variance = get_variances(se, n),
    node = names(k), 
    ) %>% 
  select(node, k, n , se, variance)

#sqrt(((variance(se1, n1)^2)/n1) + ((variance(se2, n2)^2)/n2))

# map2(
#   .x = 
#     get_variances(
#       se = get_standard_errors(glmertree_mod),
#       n = get_node_counts(glmertree_mod)[, 2]
#       ), 
#   .y = get_node_counts(glmertree_mod)[, 2], 
#   )

satterwaithe_pooled_se <- 
  function(variance1, n1, variance2, n2){
  sqrt((variance1)/n1 + (variance2)/n2)
  }

temp_pooled <- 
  satterwaithe_pooled_se(
    temp_df$variance[1], 
    temp_df$n[1], 
    temp_df$variance[2], 
    temp_df$n[2])

pooled_se_df <- 
  tibble(
    se = temp_pooled,
    new_n = temp_df$n[1] + temp_df$n[2], 
  ) %>% 
  bind_rows(temp_df[2:nrow(temp_df),])




```


```{r}
temp_df
```


```{r}
lmer1 <- 
  lmer(
  data = dat, 
  formula = 
    score ~ 
    x_lv1*z_lv1 + (1 | scid)
)
summary(lmer1)
```

```{r}
rmse(tree1)
rmse(lmer1)
AIC(tree1)
AIC(lmer1)
BIC(tree1)
BIC(lmer1)
```

```{r}
get_node_counts(tree1) 
```

```{r}
extract_node_splits(tree1)
```

```{r}
get_number_of_nodes(tree1)
```

```{r}
extract_variable_ranges(glmertree_mod = tree1)
```

```{r}
tree1$data %>% 
  mutate(
    node = .tree, 
    prediction = predict(tree1), 
    id = 1:nrow(.)
    ) %>% 
  ggplot(
    aes(x = x_lv1, y = prediction, color = node)
  ) +
  geom_point(
    #aes(size = abs(prediction - score)), 
    alpha = 0.2
    ) +
  geom_smooth(method = 'lm', se = F, color = 'black', aes(group = node)) +
  # geom_smooth(
  #   inherit.aes = F, 
  #   aes(x = x_lv1, y = prediction), 
  #   color = 'black', 
  #   se = F, 
  #   method = 'loess') + 
  facet_wrap(~node)
```

```{r}
tree1$data %>% 
  mutate(
    node = .tree, 
    prediction = predict(tree1), 
    id = 1:nrow(.)
    ) %>% 
  ggplot(
    aes(x = z_lv1, y = prediction, color = node)
  ) +
  geom_point(
    #aes(size = abs(prediction - score)), 
    alpha = 0.2
    ) +
  geom_smooth(method = 'lm', se = F, color = 'black', aes(group = node)) +
  geom_smooth(
    inherit.aes = F, 
    aes(x = z_lv1, y = prediction), 
    color = 'black', 
    se = F, 
    method = 'loess')
```


```{r}


ns_param <- 
  new_quant_param(
    type = "integer",
    range = c(10, 2000),
    inclusive = c(TRUE, TRUE),
    trans = NULL,
    label = c(ns_param = "number of level 1 units"),
    finalize = NULL
  )

js_param <- 
  new_quant_param(
    type = "integer",
    range = c(10, 200),
    inclusive = c(TRUE, TRUE),
    trans = NULL,
    label = c(js_param = "number of level 2 units"),
    finalize = NULL
  )

intx_param <- 
  new_quant_param(
    type = "integer",
    range = c(-3, 3),
    inclusive = c(TRUE, TRUE),
    trans = NULL,
    label = c(intx_param = "interaction values"),
    finalize = NULL
  )
```

```{r}
parameter_grid <- 
  grid_max_entropy(
  ns_param, 
  js_param, 
  intx_param,
  size = 100,
  original = FALSE)
```

```{r}
## make 100 data sets with a space filling design to cover all of these
sim_dat <-
  pmap(
    list(
      parameter_grid$ns_param, 
      parameter_grid$js_param, 
      parameter_grid$intx_param), 
    ~simulate_two_level_interaction(
      n = ..1, 
      j = ..2, 
      intercept_lv1 = 10.00, 
      interaction = ..3,
      main_x = 1.00, 
      main_z = 2.00,
      residual_var_sd_lv1 = 6.00,
      random_int_mean_lv2 = 5, 
      random_int_sd_lv2 = 2.00, 
      start_seed = 123
      )
  )
```

